The Galactic Chemical Evolution of Carbon: Implications for Stellar Nucleosynthesis

### 2025-03-09 carbon_paper/tex/main.tex
draft updates: new set of models with new yield scale

\newcommand{\fruity}{\texttt{\hyperlink{fruity}{Fruity}}}
\newcommand{\nugrid}{\texttt{\hyperlink{nugrid}{NuGrid}}}
\newcommand{\monash}{\texttt{\hyperlink{monash}{Monash}}}
\newcommand{\aton}{\texttt{\hyperlink{aton}{ATON}}}
\newcommand{\cfactor}{1.95}
\newcommand{\nsubgiants}{14,069}

@@

% other
\newcommand{\fmeas}{20\%}

@@

We use the sample of \apogee\ DR17 subgiants from \citet{jack}. We select stars from the ASPCAP pipeline (revision 1) within the $\log g$-$T_\text{eff}$ polygon given by
 \begin{equation}
    \begin{cases} \label{eq:subgiant_selection}
        \log \text{g} \geq 3.5 \\
        \log \text{g} \leq 0.004\,T_{\rm eff} - 15.7 \\
        \log \text{g} \leq 0.0007\,T_{\rm eff} + 0.36 \\
        \log \text{g} \leq -0.0015\,T_{\rm eff} + 12.05 \\
        \log \text{g} \geq 0.0012\,T_{\rm eff} - 2.8. \\
    \end{cases}
\end{equation}
Following \citet{jack}, we also exclude stars with the flags:
        \verb|APOGEE_MIRCLUSTER_STAR|,
        \verb|APOGEE_EMISSION_STAR|,
        \verb|APOGEE_EMBEDDEDCLUSTER_STAR|,
        \verb|APOGEE2_YOUNG_CLUSTER|,
        \verb|APOGEE2_W345|,
        \verb|APOGEE2_EB|, and
        \verb|DUPLICATE|.
We additionally remove stars with no reported (or flagged unreliable), C, Mg, or Fe abundances. These cuts yield a sample containing \nsubgiants\ subgiants.

@@

Table~\ref{tab:fiducial_mod} summarizes our yield choices. 
Following \citet{james+23}, we integrate yields and our GCE models using the publicly available Versatile Integrator for Chemical Evolution (\VICE, \citealt{JW20}). We use the O, Mg, and Fe yields recommended by \citet{david_fe} based on measurements of the mean CCSN Fe yield \citep{rodriguez+23} and APOGEE chemical abundances.
Our N yield is scaled from \citep{james+23}.
We assume a \citet{kroupa01} initial mass function (IMF).

\begin{table}
	\centering
    \caption[]{Solar abundance scale and fiducial yields (in units of stellar population birth mass). See section \ref{sec:agb} for the definition of \fruity. The solar abundance scale is \citet{magg+22} + 0.04 dex suggested by \citet{david_fe}.
    \dbnote{any tips to make this table a little bit smaller?}
    }
	\label{tab:fiducial_mod}

@@

    \caption[]{\textbf{Left} The integrated \agb\ C yield $\Ycagb$ as a function of metallicity for each of the \agb\ yield tables.
    \textbf{Right} cumulative C return fraction as a function of age for a solar metallicity single stellar population. The dashed black line shows the cumulative return fraction of type Ia supernovae ($\propto t^{-1.1}$) for comparison. The minimum of \aton{} is at $y( 0.30\,{\rm Gyr})/y(t_{\rm end})=-7.81$ and is large as the net yield is close to zero.
}

@@

	\label{tab:agb}
    \begin{tabular}{c  ccc  c p{4cm} p{4cm}} % four columns, alignment for each
		\hline 
        \agb\ table 
                & $y_{\rm C, \odot}^{\rm AGB}\times10^4$ %& y
                & $\zetao^{\rm AGB}\times 10^4$ %& y
                & $\zetai^{\rm AGB}\times 10^4$
                &  $f_\odot^{\rm AGB}$
                & masses ($\Mo$) & metallicities ($Z$)\\
        \hline
        \fruity 
                & 3.229
                &  $3.8\pm0.3$
                & $-3.5\pm0.3$
                & 0.14
                & 1.3, 1.5, 2, 2.5, 3, 4, 5, 6
                & 0.0001, 0.0003, 0.001, 0.002, 0.003, 0.006, 0.008, 0.01, 0.014, 0.02
                \\
        \aton 
                & 0.2851
                & $1.4\pm1.8$
                & $-10. \pm 3$
                & 0.05
                & 1.5, 2, 2.5, 3, 3.5, 4, 4.5, 5, 6, 6.5, 7
                & 0.0003, 0.001, 0.002, 0.004, 0.008, 0.014, 0.04
                \\
        \monash 
                &  3.444
                & $2.8 \pm 0.5$
                & $-11.0\pm 1.0$
                & 0.10
                & 1, 1.25, 1.5, 1.75, 2.25, 2.5, 2.75, 3, 3.25, 3.5, 3.75, 4, 4.5, 5, 5.5, 6, 7 
                & 0.0028, 0.007, 0.014, 0.03
                \\
        \nugrid 
                & 10.95
                & $8.3\pm 1.9$
                & $-4.6\pm1.7$
                & 0.30
                & 1, 1.65, 2, 3, 4, 5, 6, 7
                &  0.0001, 0.001, 0.006, 0.01, 0.02
                \\
		\hline
	\end{tabular}
\end{table*}

@@

\begin{figure*}
    \centering
    \includegraphics{cc_yields.pdf}
    \caption[]{
    \dbnote{might be interesting to plot every CCSNe yield used in this paper in light grey to show strength of our constraint}
        C yields from high-mass stars.
        \textbf{Left} The IMF-weighted \cc\ yield of C as a function of metallicity.
        \textbf{Right} The \cc\ [C/Mg] abundance ratio, defined in Eq.~\ref{eq:c_mg_cc}. The black line is the derived C yield from section~\ref{sec:mcmc_results}. Yields are shown for tables from 
    \citet[red triangles]{WW95}, \citet[orange square and diamond]{sukhbold+16}, 
    \citet[green stars]{NKT13}, and \citet[blue circles]{LC18}. \citet{sukhbold+16} report yields for different black hole landscapes, while \citet{LC18} provide yields at different rotational velocities.
    In the left panel, the pink line denotes $\Ycagb$ from \fruity{} for comparison. All models include wind yields. 
}
    \label{fig:y_cc}
\end{figure*}

@@

We use the radial migration prescription described in appendix C of \citet{dubay+24}.\footnote{Not shown here, we also explored variations of temporal, spatial resolution, migration strength, and the mass lifetimre relation. We found these do not affect median trends significantly.}
We do not account for radial gas flows.
Not shown here, we also explore migration based on random walks and the \texttt{h277} hydrodynamical
simulation results\footnote{(with simulation parameters as in \citealt{bird+21}; see also \citealt{christensen12, zolotov12, loebman12, BZ14} \dbnote{is this okay as footnote?} }, which leaves our qualitative conclusions unchanged. 
The full impact of the details of a galaxy's dynamical history on its chemical evolution is still unknown.

As the strength of outflows controls the resulting $\alpha$-element abundances, we extend \JJ and create a metallicity gradient by defining
\begin{equation}\label{eq:mass_loading}
\eta(R) = \frac{y_{\alpha}^{\rm cc}}{Z_{\alpha}(R)} -1 + r + \tau_{\star} / \tau_{\rm sfh} 
\end{equation}
where 
\begin{equation}
    \log Z_{\alpha}(R) = \log Z_{\alpha,\ \odot} + 
    0.29 + 
    \begin{cases}
        -0.015(R-5) & R < 5 \\
        -0.09(R-5) & R \geq 5
    \end{cases}
\end{equation}
is adapted from \citet{hayden+14}.  We approximate $r=0.4$, and $\tau_\star/\tau_{\rm sfh} = 0.0$ .
This choice of $\eta(R)$ results in a [$\alpha$/H] gradient consistent with Milky Way observations \citep[e.g.][]{hayden+14, weinberg+19, frinchaboy+13}.
If we change our assumed $y_{\rm Mg}$, the values of $\eta$ will change similarly to maintain the correct chemical trends.

@@

We adopt the following priors
\begin{subequations}
\begin{align}
    \alpha &\sim N(1, 1) \\
    \zeta^{(0)} &\sim N(2, 1) \\
    \zeta^{(1)} &\sim N(0, 1) \\
    \zeta^{(2)} &\sim N(0, 4) \\
    \ln \sigma _{\rm int}&\sim N(-3, 1) \\
\end{align}
\end{subequations}
We run the MCMC using Turing.jl with a No-U-turn sampler (acceptance rate of 0.65), combining 16 independent chains with 3,000 steps each for a total of 48,000 samples.

@@

\begin{figure}
\centering
\includegraphics{figures/mcmc_corner.pdf}
\caption[]{
A corner plot of the posterior samples from the MCMC simulation for the fiducial + \fruity\ model fit to the binned mean trends.
$\alpha$ represents the scale factor for the AGB yields, and $\zetao$, $\zetai$ and $\zetaii$ represent the constant, linear, and quadratic components of the CCSN yield.
See section~\ref{sec:mcmc_methods} for a description of the methods.
}

@@

    \caption[]{
    \textbf{Left:} Posterior distribution of $\fagb$ from MCMC samples for each model we show. Regardless of assumptions, the best values of $\fagb$ range from about 0.1 to 0.35 and in all cases is less than 0.5.
    \textbf{Right:} The final total C yield (CCSN + AGB) for the median parameters from MCMC fits for each model. Additionally, we show individual samples from the \fruity{} \ MCMC model as faint blue lines.
    \dbnote{mark alpha=1.}
    }

@@

\begin{table*}

    \caption{
    Best-fit parameters (medians and 16-84th percentile errors) from MCMC analysis for various models discussed.
    The columns are:  modelname \textit{model}, best fit reduced $\chi^2$, best fit log posterior probability $\log p$, AGB scaling $\aagb$, 
    \dbnote{Not sure if we should use analytic, nugrid, shifted fruity or normal fruity yields as fiducial for this section, e.g. for eta, lateburst, twoinfall, etc...}}
    \label{tab:mcmc_results}
{ 
\renewcommand{\baselinestretch}{1.2}
    \begin{tabular}{l l l l l l l l l l l} 
    \hline
    model            & $\chi2$  & $\log p$ & $\aagb$ & $\zetao$ & $\zetai$ & $\zetaii$ & $\sigma_{\rm int}$ & $\fagb$ & $\Yct$ & $\zeta_{\rm 1, tot}$\\
\hline
fruity           &      6.9 &    20.06 & $1.96^{+0.21}_{-0.21}$  &  $2.01^{+0.08}_{-0.08}$  &  $2.20^{+0.15}_{-0.15}$  &  $2.73^{+0.31}_{-0.31}$  &  $0.08^{+0.02}_{-0.01}$  &  $0.27^{+0.03}_{-0.03}$  &  $2.75^{+0.02}_{-0.02}$  &  $1.52^{+0.13}_{-0.13}$\\ 
fruity m0.7      &      6.3 &    28.60 & $1.10^{+0.10}_{-0.10}$  &  $2.33^{+0.04}_{-0.04}$  &  $1.71^{+0.11}_{-0.11}$  &  $2.89^{+0.27}_{-0.27}$  &  $0.06^{+0.01}_{-0.01}$  &  $0.17^{+0.01}_{-0.01}$  &  $2.80^{+0.01}_{-0.02}$  &  $1.37^{+0.10}_{-0.10}$\\ 
aton             &     10.5 &    10.66 & $1.56^{+0.24}_{-0.24}$  &  $2.50^{+0.04}_{-0.04}$  &  $3.37^{+0.32}_{-0.32}$  &  $2.50^{+0.40}_{-0.39}$  &  $0.11^{+0.02}_{-0.02}$  &  $0.08^{+0.01}_{-0.01}$  &  $2.72^{+0.02}_{-0.02}$  &  $1.81^{+0.17}_{-0.17}$\\ 
monash           &     10.8 &     6.86 & $2.06^{+0.37}_{-0.39}$  &  $1.92^{+0.16}_{-0.15}$  &  $3.68^{+0.42}_{-0.45}$  &  $3.52^{+0.47}_{-0.47}$  &  $0.13^{+0.03}_{-0.02}$  &  $0.23^{+0.05}_{-0.05}$  &  $2.49^{+0.05}_{-0.05}$  &  $1.41^{+0.20}_{-0.19}$\\ 
nugrid           &      6.1 &    23.68 & $1.00^{+0.10}_{-0.10}$  &  $1.75^{+0.10}_{-0.10}$  &  $1.58^{+0.12}_{-0.12}$  &  $3.19^{+0.31}_{-0.30}$  &  $0.07^{+0.02}_{-0.01}$  &  $0.32^{+0.03}_{-0.03}$  &  $2.58^{+0.02}_{-0.02}$  &  $1.12^{+0.12}_{-0.13}$\\ 
analytic         &      5.1 &    29.80 & $0.43^{+0.04}_{-0.04}$  &  $2.33^{+0.04}_{-0.04}$  &  $1.57^{+0.10}_{-0.10}$  &  $2.69^{+0.27}_{-0.26}$  &  $0.06^{+0.01}_{-0.01}$  &  $0.15^{+0.01}_{-0.01}$  &  $2.75^{+0.01}_{-0.01}$  &  $1.15^{+0.10}_{-0.11}$\\ 
eta2             &      6.6 &    24.28 & $0.47^{+0.05}_{-0.04}$  &  $2.24^{+0.05}_{-0.05}$  &  $1.45^{+0.09}_{-0.10}$  &  $2.95^{+0.32}_{-0.32}$  &  $0.07^{+0.02}_{-0.01}$  &  $0.17^{+0.02}_{-0.02}$  &  $2.71^{+0.02}_{-0.01}$  &  $0.98^{+0.09}_{-0.09}$\\ 
lateburst        &      8.0 &    21.72 & $0.56^{+0.05}_{-0.05}$  &  $2.25^{+0.05}_{-0.05}$  &  $1.75^{+0.18}_{-0.18}$  &  $2.55^{+0.37}_{-0.36}$  &  $0.08^{+0.02}_{-0.01}$  &  $0.20^{+0.02}_{-0.02}$  &  $2.81^{+0.02}_{-0.02}$  &  $1.19^{+0.18}_{-0.18}$\\ 
twoinfall        &      6.3 &    17.12 & $0.54^{+0.06}_{-0.06}$  &  $2.31^{+0.07}_{-0.07}$  &  $1.72^{+0.19}_{-0.20}$  &  $1.69^{+0.30}_{-0.30}$  &  $0.09^{+0.02}_{-0.02}$  &  $0.19^{+0.02}_{-0.02}$  &  $2.85^{+0.02}_{-0.03}$  &  $1.18^{+0.20}_{-0.20}$\\ 
fruitylin       &    &    & $1.95$  &  $2.10^{+0.02}_{-0.02}$  &  $1.55^{+0.08}_{-0.08}$  &     &  $0.09^{+0.02}_{-0.01}$  &  $0.26^{+0.00}_{-0.00}$  &  $2.84^{+0.02}_{-0.02}$  &  $0.87^{+0.08}_{-0.08}$\\ 
analyticlin     &    &    & $0.43$  &  $2.41^{+0.02}_{-0.02}$  &  $0.89^{+0.09}_{-0.09}$  &     &  $0.10^{+0.02}_{-0.01}$  &  $0.15^{+0.00}_{-0.00}$  &  $2.84^{+0.02}_{-0.02}$  &  $0.46^{+0.09}_{-0.09}$\\ 
\hline
total & &   &  -  &  $2.26^{+0.11}_{-0.37}$  &  $1.74^{+1.53}_{-0.24}$  &  $2.79^{+0.49}_{-0.58}$  &  $0.08^{+0.03}_{-0.02}$  &  $0.19^{+0.09}_{-0.04}$  &  $2.74^{+0.07}_{-0.16}$  &  $1.26^{+0.32}_{-0.24}$\\
\hline
    \end{tabular}

@@

    \caption[]{
        Similar to Fig.~\ref{fig:zeta_f}, except for \caafe\ for a variety of models.
        {\bf Left} models where both the \agb\ fraction and the CCSNe slope are varied simultaneously.
        {\bf Middle} models where the \agb\ yields are shifted by some factor in mass.
        {\bf Right} alternate star formations and a model where yields and outflows are $\sim$ doubled.
    \dbnote{update caption here}
    }
    \label{fig:sims_degens}
\end{figure*}

@@

    \caption[]{
        Similar to Fig.~\ref{fig:zeta_f} except showing the mean tracks for different best-fit AGB yield tables with best-fit CCSNe parameters. Variations in the \caafe\ plane are due to the different total AGB C yield and variations in the mass-dependence of each yield table.
    \dbnote{use actual best fit median trends here instead of inferred yields? Update labels, remove one of analytic / fruity m0.7}.
    }
    \label{fig:agb_predictions}
\end{figure*}

@@

We also consider a two-infall like model as presented in \dbadd{dubay + 24}, which is defined as.
\begin{equation}\label{twoinfall}
\dot{\Sigma}_{\rm in} \propto e^{-t/\tau_1} + A \theta(t - t_{2}) e^{-t/\tau_2}
\end{equation}
where $\tau_1=\#\,$Gyr, $\tau_2=4\,$Gyr, $A=\Sigma_{\rm thin} / \Sigma_{\rm thick}$ \dbadd{explanation}, $t_2=4$, and the star formation also abruptly transitions from $\nu=2$/Gyr to $\nu=1$/Gyr at $t=t_1$?

@@

\begin{table}
	\centering
    \caption[]{Description of the models presented in this paper.}
	\label{tab:model_parameters}

>>>>

\newcommand{\fruity}{\texttt{\hyperlink{fruity}{Fruity}}}
\newcommand{\nugrid}{\texttt{\hyperlink{nugrid}{NuGrid}}}
\newcommand{\monash}{\texttt{\hyperlink{monash}{Monash}}}
\newcommand{\aton}{\texttt{\hyperlink{aton}{ATON}}}
\newcommand{\cfactor}{2.40}
\newcommand{\nsubgiants}{14,066}

@@

% other

@@

We use the sample of \apogee\ DR17 subgiants from \citet{jack}. We select stars from the ASPCAP pipeline (revision 1) within the $\log g$-$T_\text{eff}$ polygon given by
 \begin{equation}
    \begin{cases} \label{eq:subgiant_selection}
        \log \text{g} \geq 3.5 \\
        \log \text{g} \leq 0.004\,T_{\rm eff} - 15.7 \\
        \log \text{g} \leq 0.0007\,T_{\rm eff} + 0.36 \\
        \log \text{g} \leq -0.0015\,T_{\rm eff} + 12.05 \\
        \log \text{g} \geq 0.0012\,T_{\rm eff} - 2.8. \\
    \end{cases}
\end{equation}
Following \citet{jack}, we also exclude stars with the flags:
        \verb|APOGEE_MIRCLUSTER_STAR|,
        \verb|APOGEE_EMISSION_STAR|,
        \verb|APOGEE_EMBEDDEDCLUSTER_STAR|,
        \verb|APOGEE2_YOUNG_CLUSTER|,
        \verb|APOGEE2_W345|,
        \verb|APOGEE2_EB|, and
        \verb|DUPLICATE|.
We additionally remove stars with no reported (or flagged unreliable), C, N, Mg, or Fe abundances. These cuts yield a sample containing \nsubgiants\ subgiants.

@@

Table~\ref{tab:fiducial_mod} summarizes our yield choices. 
Following \citet{james+23}, we integrate yields and our GCE models using the publicly available Versatile Integrator for Chemical Evolution (\VICE, \citealt{JW20}). Our solar abundance scale is from \citet{magg+22} with a 0.04 dex gravitational settling correction. Also from \citet{magg+22}, we adopt $\Zo = 0.0176$. We use the O, Mg, and Fe yields recommended by \citet{david_fe} based on measurements of the mean CCSN Fe yield \citep{rodriguez+23} and APOGEE chemical abundances.
Our N yield is scaled from \citep{james+23}.
We assume a \citet{kroupa01} initial mass function (IMF).

\begin{table}
	\centering
    \caption[]{Solar abundance scale and fiducial yields (in units of stellar population birth mass). See section \ref{sec:agb} for the definition of \fruity. The solar abundance scale is \citet{magg+22} + 0.04 dex suggested by \citet{david_fe}.
        \dbnote{Technically, I believe this abundance scale is off by the hydrogen 1 atomic weight. But this is < the systematic correction so I think this is negligable?}.
    \dbnote{any tips to make this table a little bit smaller?}
    }
	\label{tab:fiducial_mod}

@@

    \caption[]{\textbf{Left} The integrated \agb\ C yield $\Ycagb$ as a function of metallicity for each of the \agb\ yield tables.
        \textbf{Right} cumulative C return fraction as a function of age for a metallicity of ${\rm [M/H]}=-0.1$ single stellar population. The dashed black line shows the cumulative return fraction of type Ia supernovae ($\propto t^{-1.1}$) for comparison. The minimum of \aton{} is at $y( 0.30\,{\rm Gyr})/y(t_{\rm end})=-3$ and is large as the net yield is close to zero.
}

@@

	\label{tab:agb}
    \begin{tabular}{c  ccc  c p{4cm} p{4cm}} % four columns, alignment for each
		\hline 
        \agb\ table 
                & $y_{\rm C, \odot}^{\rm AGB}\times10^4$ %& y
                & $\zetao^{\rm AGB}\times 10^4$ %& y
                & $\zetai^{\rm AGB}\times 10^4$
                &  $f_\odot^{\rm AGB}$
                & masses ($\Mo$) & metallicities ($Z$)\\
        \hline
        \fruity 
                & 3.11
                &  $3.7\pm0.3$
                & $-3.5\pm0.3$
                & 0.13
                & 1.3, 1.5, 2, 2.5, 3, 4, 5, 6
                & 0.0001, 0.0003, 0.001, 0.002, 0.003, 0.006, 0.008, 0.01, 0.014, 0.02
                \\
        \aton 
                & -0.009
                & $1.0\pm1.8$
                & $-10. \pm 3$
                & 0.04
                & 1.5, 2, 2.5, 3, 3.5, 4, 4.5, 5, 6, 6.5, 7
                & 0.0003, 0.001, 0.002, 0.004, 0.008, 0.014, 0.04
                \\
        \monash 
                &  2.96
                & $2.3 \pm 0.5$
                & $-11.0\pm 1.0$
                & 0.08
                & 1, 1.25, 1.5, 1.75, 2.25, 2.5, 2.75, 3, 3.25, 3.5, 3.75, 4, 4.5, 5, 5.5, 6, 7 
                & 0.0028, 0.007, 0.014, 0.03
                \\
        \nugrid 
                & 9.25
                & $8.1\pm 1.9$
                & $-4.6\pm1.7$
                & 0.29
                & 1, 1.65, 2, 3, 4, 5, 6, 7
                &  0.0001, 0.001, 0.006, 0.01, 0.02
                \\
		\hline
	\end{tabular}
\end{table*}

@@

\begin{figure*}
    \centering
    \includegraphics{cc_yields.pdf}
    \caption[]{
    \dbnote{might be interesting to plot every CCSNe yield used in this paper in light grey to show strength of our constraint}
    \dbnote{I may change the piecewise model to be linear in log-log space instead of log-linear space}
        C yields from high-mass stars.
        \textbf{Left} The IMF-weighted \cc\ yield of C as a function of metallicity.
        \textbf{Right} The \cc\ [C/Mg] abundance ratio, defined in Eq.~\ref{eq:c_mg_cc}. The black line is the derived C yield from section~\ref{sec:mcmc_results}. Yields are shown for tables from 
    \citet[red triangles]{WW95}, \citet[orange square and diamond]{sukhbold+16}, 
    \citet[green stars]{NKT13}, and \citet[blue circles]{LC18}. \citet{sukhbold+16} report yields for different black hole landscapes, while \citet{LC18} provide yields at different rotational velocities.
    In the left panel, the pink line denotes $\Ycagb$ from \fruity{} for comparison. All models include wind yields. 
}
    \label{fig:y_cc}
\end{figure*}

@@

For radial migration of stars, inspired by \citet{frankel18}, we sample the change of radii of stars from a gaussian distribution with standard deviation $\sigma = 3.6\,{\rm kpc} ((t_{\rm end} - t_{\rm birth})/8\,{\rm Gyr})^{0.5}$, where $t_{\rm birth}$ is the birth time of the SSP and $t_{\rm end}=13.2$\,Gyr is the simulation end time.
Stars migrate to their final position with a $\sqrt{t}$ dependence, consistent with diffusion of angular momentum \citep{frankel18, frankel20}. If a star's would move past $R=0$ or $R=20\,$kpc, the star reflects off these boundaries instead with the same velocity.% 
\footnote{Not shown here, we also explored variations of temporal, spatial resolution, migration strength, and the mass lifetime relation. We found these do not affect median trends significantly.}
\dbnote{ Final set of models will use the radial migration prescription described in appendix C of {dubay+24} instead. I have checked that changes to derived parameters for the fiducial model is within the parameter uncertanties, so nothing substantial should change. }.
We do not account for radial gas flows.
Not shown here, we also explore migration based on random walks and the \texttt{h277} hydrodynamical
simulation results\footnote{(with simulation parameters as in \citealt{bird+21}; see also \citealt{christensen12, zolotov12, loebman12, BZ14} \dbnote{is this okay as footnote?} }, which leaves our qualitative conclusions unchanged. 
The full impact of the details of a galaxy's dynamical history on its chemical evolution is still unknown.

As the strength of outflows controls the resulting equilibrium $\alpha$-element abundances, we extend \JJ and create a metallicity gradient by defining
\begin{equation}\label{eq:mass_loading}
\eta(R) = \frac{y_{\alpha}^{\rm cc}}{Z_{\alpha}(R)} -1 + r %+ \tau_{\star} / \tau_{\rm sfh} 
\end{equation}
where 
\begin{equation}
    \log Z_{\alpha}(R) = \log Z_{\alpha,\ \odot} + 
    0.29 + 
    \begin{cases}
        -0.015(R-5) & R < 5 \\
        -0.09(R-5) & R \geq 5
    \end{cases}
\end{equation}
is adapted from \citet{hayden+14}.  We approximate $r=0.4$. %, and $\tau_\star/\tau_{\rm sfh} = 0.0$ .
This choice of $\eta(R)$ results in a [$\alpha$/H] gradient consistent with Milky Way observations \citep[e.g.][]{hayden+14, weinberg+19, frinchaboy+13}.
If we change our assumed $y_{\rm Mg}$, the values of $\eta$ will change similarly to maintain the correct chemical trends.

@@

We adopt the following priors
\begin{subequations}
\begin{align}
    \alpha &\sim N(1, 1) \\
    \zeta^{(0)} &\sim N(2, 1) \\
    \zeta^{(1)} &\sim N(0, 1) \\
    \zeta^{(2)} &\sim N(0, 4) \\
    \ln \sigma _{\rm int}&\sim N(-3, 1)
\end{align}
\end{subequations}
We run the MCMC using Turing.jl with a No-U-turn sampler (acceptance rate of 0.65), combining 16 independent chains with 3,000 steps each for a total of 48,000 samples.

@@

\begin{figure}
\centering
\includegraphics{figures/mcmc_corner.pdf}
\caption[]{
A corner plot of the posterior samples from the MCMC simulation for the analytic model fit to the binned mean trends.
$\alpha$ represents the scale factor for the AGB yields, and $\zetao$, $\zetai$ and $\zetaii$ represent the constant, linear, and quadratic components of the CCSN yield (all scaled by $10^{-3}$). $\sigma_{\rm int}$ is the intrensic scatter.
See section~\ref{sec:mcmc_methods} for a description of the methods.
}

@@

    \caption[]{
        \textbf{Left:} Posterior distribution of $\fagb$ from MCMC samples for each model we show. Regardless of assumptions, the best values of $\fagb$ range from about 0.1 to 0.35 and in all cases is less than 0.5. The black X marks the predicted value of $\fagb$ assuming our fiducial yield scale (as in Table~\ref{tab:agb}).
    \textbf{Right:} The final total C yield (CCSN + AGB) for the median parameters from MCMC fits for each model. Additionally, we show individual samples from the \fruity{} \ MCMC model as faint blue lines.
    }

@@

\begin{table*}
    \caption{
        Best-fit parameters (medians and 16-84th percentile errors) from MCMC analysis for various models discussed.
        The columns are:  modelname \textit{model}, best fit reduced $\chi^2$, best fit log posterior probability $\log p$, AGB scaling $\aagb$, CCSN constant, linear, and quadratic coefficients times $10^3$ $\zetao$, $\zetai$, $\zetaii$, the intrensic scatter $\sigma_{\rm int}$, the AGB fraction $\fagb$, the total C yield at solar metallicity $\Yct$, and the total C yield at solar metallicity $\zeta_{\rm 1, tot}$.
    }
    \label{tab:mcmc_results}

{ 
\renewcommand{\baselinestretch}{1.2}
    \begin{tabular}{l l l l l l l l l l l} 
    \hline
    model            & $\chi2$  & $\log p$ & $\aagb$ & $\zetao$ & $\zetai$ & $\zetaii$ & $\sigma_{\rm int}$ & $\fagb$ & $\Yct$ & $\zeta_{\rm 1, tot}$\\
\hline
\fruity          &      7.4 &    18.43 & $2.41^{+0.26}_{-0.27}$  &  $1.90^{+0.10}_{-0.09}$  &  $2.28^{+0.15}_{-0.16}$  &  $2.59^{+0.30}_{-0.30}$  &  $0.08^{+0.02}_{-0.01}$  &  $0.32^{+0.03}_{-0.04}$  &  $2.79^{+0.02}_{-0.02}$  &  $1.43^{+0.12}_{-0.13}$\\ 
\aton            &     14.9 &     5.30 & $1.71^{+0.34}_{-0.34}$  &  $2.55^{+0.05}_{-0.05}$  &  $3.19^{+0.40}_{-0.40}$  &  $1.92^{+0.45}_{-0.44}$  &  $0.14^{+0.03}_{-0.02}$  &  $0.06^{+0.01}_{-0.01}$  &  $2.72^{+0.03}_{-0.03}$  &  $1.48^{+0.20}_{-0.19}$\\ 
\monash          &     15.4 &     2.24 & $2.06^{+0.52}_{-0.54}$  &  $2.03^{+0.19}_{-0.18}$  &  $3.82^{+0.64}_{-0.66}$  &  $3.48^{+0.57}_{-0.59}$  &  $0.15^{+0.03}_{-0.02}$  &  $0.19^{+0.05}_{-0.05}$  &  $2.50^{+0.07}_{-0.07}$  &  $1.55^{+0.21}_{-0.22}$\\ 
\nugrid          &      5.8 &    24.19 & $1.21^{+0.11}_{-0.11}$  &  $1.58^{+0.11}_{-0.11}$  &  $1.58^{+0.11}_{-0.11}$  &  $3.16^{+0.29}_{-0.28}$  &  $0.07^{+0.02}_{-0.01}$  &  $0.38^{+0.04}_{-0.04}$  &  $2.56^{+0.02}_{-0.02}$  &  $1.02^{+0.11}_{-0.11}$\\ 
\fruity\ m0.7    &      4.5 &    32.86 & $1.39^{+0.11}_{-0.10}$  &  $2.25^{+0.04}_{-0.04}$  &  $1.55^{+0.09}_{-0.08}$  &  $2.54^{+0.23}_{-0.22}$  &  $0.05^{+0.01}_{-0.01}$  &  $0.21^{+0.02}_{-0.01}$  &  $2.83^{+0.01}_{-0.01}$  &  $1.12^{+0.09}_{-0.09}$\\ 
\fruity\ linear  &   3036 &    16.18 & $2.40^{+0.00}_{-0.00}$  &  $1.99^{+0.02}_{-0.02}$  &  $1.68^{+0.08}_{-0.09}$  &     &  $0.10^{+0.02}_{-0.02}$  &  $0.31^{+0.00}_{-0.00}$  &  $2.88^{+0.02}_{-0.02}$  &  $0.84^{+0.08}_{-0.09}$\\ 
$y\rightarrow 2y$ &      6.0 &    20.61 & $2.51^{+0.25}_{-0.25}$  &  $1.83^{+0.09}_{-0.09}$  &  $2.00^{+0.12}_{-0.12}$  &  $2.41^{+0.29}_{-0.29}$  &  $0.08^{+0.02}_{-0.01}$  &  $0.34^{+0.03}_{-0.03}$  &  $2.76^{+0.02}_{-0.02}$  &  $1.12^{+0.08}_{-0.08}$\\ 
lateburst        &     18.7 &     8.35 & $2.41^{+0.35}_{-0.36}$  &  $2.00^{+0.12}_{-0.12}$  &  $2.92^{+0.34}_{-0.34}$  &  $3.51^{+0.66}_{-0.65}$  &  $0.13^{+0.02}_{-0.02}$  &  $0.31^{+0.04}_{-0.04}$  &  $2.89^{+0.03}_{-0.03}$  &  $2.07^{+0.32}_{-0.32}$\\ 
twoinfall        &     10.6 &    18.05 & $2.03^{+0.21}_{-0.21}$  &  $2.05^{+0.08}_{-0.08}$  &  $2.65^{+0.20}_{-0.20}$  &  $3.52^{+0.35}_{-0.36}$  &  $0.09^{+0.02}_{-0.01}$  &  $0.27^{+0.03}_{-0.03}$  &  $2.80^{+0.02}_{-0.02}$  &  $1.94^{+0.18}_{-0.19}$\\ 
SN Ia 1.2        &      9.3 &    13.10 & $3.29^{+0.43}_{-0.45}$  &  $1.57^{+0.16}_{-0.15}$  &  $2.73^{+0.22}_{-0.23}$  &  $2.72^{+0.35}_{-0.35}$  &  $0.10^{+0.02}_{-0.02}$  &  $0.44^{+0.06}_{-0.06}$  &  $2.79^{+0.02}_{-0.02}$  &  $1.58^{+0.14}_{-0.14}$\\

\hline
    \end{tabular}

@@

    \caption[]{
        Similar to Fig.~\ref{fig:zeta_f}, except for \caafe\ for a variety of models.
        {\bf Left} models for AGB fractions of 0.1, 0.25 (fiducial), and 0.4. 
        {\bf Middle} models where the \agb\ yields are shifted by a factor in mass.
        {\bf Right} alternate star formations histories (lateburst and twoinfall) and a model with all yields doubled.
    }
    \label{fig:sims_degens}
\end{figure*}

@@

    \caption[]{
        Similar to Fig.~\ref{fig:zeta_f} except showing the mean tracks for different best-fit AGB yield tables with best-fit CCSNe parameters. Variations in the \caafe\ plane are due to the different total AGB C yield and variations in the mass-dependence of each yield table.
    }
    \label{fig:agb_predictions}
\end{figure*}

@@

We also consider a two-infall like model as presented in \citep{dubay+24},
\begin{equation}\label{twoinfall}
\dot{\Sigma}_{\rm in} \propto e^{-t/\tau_1} + A \theta(t - t_{2}) e^{-t/\tau_2}
\end{equation}
where $\tau_1=1\,$Gyr, $\tau_2=4\,$Gyr, $t_2=4$\,Gyr, and the the amplitude is given by the ratio between the thick and thin disk in

@@

\begin{table}
	\centering
        \caption[]{Description of the models presented in this paper. \dbnote{none of these are accurate currently}}
	\label{tab:model_parameters}
